---
title: "Getting Started with Binomial Distribution"
author: "ting ling"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial Distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution
The package `"binomial"` is an implementation for simulating probabilities about the number of successes in a fixed number of random trials performed under identical conditions, and to summarize the statistic of the binomial distribution. Also, providing a visualiztion the relative probability in the binomial distribution.


## Main Binomial Functions
- `bin_choose()` calculates the number of
combinations in the number of `k` successes among the `n` trials.

```{r}
bin_choose(n = 5, k = 2)
```

- `bin_probability` calculates the probability that `k` successes with `p` probability can occur in the `n` trials.

```{r}
bin_probability(k = 2,n = 5, p = 0.5)
```

- `bin_distribution` creates a data frame to list a binomial probability distribution. 

`plot()` illustrates the barplot of the binomial distribution
```{r}
dis1 <- bin_distribution(n = 5, p = 0.5)
dis1
plot(dis1)
```

- `bin_cumulative()` creates a data frame to list a binomial probability and cumulative probability distribution.

`plot()` illustrates the line graph of the binomial cumulative distribution.

```{r}
dis2 <- bin_cumulative(n = 5, p = 0.5)
dis2
plot(dis2)
```

- `bin_variable` calculates a binomial random variable object.

`summary()` lists the summarized statistics of variable.

```{r}
bin1 <- bin_variable(n = 10, p = 0.3)
bin1
```

```{r}
bin1 <- bin_variable(n = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

- Functions of measures
These functions contains the statistics of the binomial distrbution as mean, variance, mode, skewness, kurtosis.

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
